Import_JazEmData

### 2024-03-27 Code/Import_JazEmData.Rmd
tidied variable names

# Import and tidy emission data columns
```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "MultiCulti", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

JazSpec <- JazSpec %>% 
mutate(ObsDate = ymd(ObsDate),
       Par_ue = as.numeric(Par_ue),
       WL = as.factor(WL))
```

@@

# Get 1 mean emission count for each wavelength after rounding for a resolution of 1 nm   
```{r tidy to get one count for each wavelength}
JazSpecTrim <- JazSpecTrim %>% 
   group_by(MultiCulti, Par_ue, WL, Wavelength) %>%
  mutate(MCEm_nm = round(Wavelength)) %>%
  ungroup() %>%
  group_by(FilenameJaz, MultiCulti, Par_ue, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
  summarise(MeanEmission = mean(Counts)) %>%
  ungroup() %>%
  mutate(Emission = round(MeanEmission, digits = 1),
         MC = MultiCulti,
         SetPar_uE = Par_ue,
         MC_SpectralID = paste(MC,WL, sep = "_")) %>% 
  select(-c(MeanEmission))

>>>>

# Import and tidy emission data columns
```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "MultiCulti", "SetPar_uE", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

JazSpec <- JazSpec %>% 
mutate(ObsDate = ymd(ObsDate),
       SetPar_uE = as.numeric(SetPar_uE),
       WL = as.factor(WL))
```

@@

# Get 1 mean emission count for each wavelength after rounding for a resolution of 1 nm   
```{r tidy to get one count for each wavelength}
JazSpecTrim <- JazSpecTrim %>% 
   group_by(MultiCulti, SetPar_uE, WL, Wavelength) %>%
  mutate(MCEm_nm = round(Wavelength)) %>%
  ungroup() %>%
  group_by(FilenameJaz, MultiCulti, SetPar_uE, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
  summarise(MeanEmission = mean(Counts)) %>%
  ungroup() %>%
  mutate(Emission = round(MeanEmission, digits = 1),
         MC = MultiCulti,
         MC_SpectralID = paste(MC,WL, sep = "_")) %>% 
  select(-c(MeanEmission))
